Can Auxiliary Indicators Improve COVID-19 Forecasting and Hotspot Prediction?

### 2021-06-21 forecast/paper/supplement-text.tex
Add extra leading/lagging text to supplement, rebuild.

>>>>

In calculating the CCF and the associated leadingness and laggingness scores, we
have used the finalized data, and we look at the behavior when $t$ is the
target date of the forecast. That is we are using the same data to
evaluate predictive accuracy as to determine
leadingness and laggingness. It should be noted that the leadingness of the
indicator at the time the model is trained may also be important. Thus, we could
calculate separate leadningness and laggingness scores for the trained model and
for the evaluation data and examine their combination in some way. We do not
pursue this combination further and leave this question for future work.
